\section{Introduction}

%chris's intro stuff
\subsection{Emma Watson and Malware}
On September 10th 2012, MacAfee released a report detailing a list of the top 20
celebrities that it believed were the most risky to search for on the internet\cite{mac-watson}.
The report specifies a number of threats from risky web sites, such as malware,
phishing, and spam, and determined that Emma Watson was the most risky celebrity
to search for on the web with more than 12.6\% chance of a site being malicious
when searching for her name combined with phrases such as "free download".

The hypothesis suggested in the MacAfee report is that trending topics have
malicious web pages crafted specifically to target the topic, and this is the
hypothesis that will be investigated in the project.

Before investigating if malware is targed at trending topics, it is necessary to
invstigate exactly what constitutes a trending toic. "Trending topic" is a term
that originates from Twitter, where statistics are collected on users tweeting
with a given hashtag and used to determine popular hashtags, presented in the
user interface a "trending topic". When discussing trending topics in this
report, other sources of trends and popular subjects will also be considered as
trending topics.

To make it possible to invesitgate the hypothesis proposed above a framework
will be designed and build to automatically gather trends, search for URLs
relating to the trends, and then attempt to detect whether the URL is hosting
malicious content. The data will then be collected into a database, allowing the
hypothesis to be tested. Results will be reported using a web interface that
will also be capable of monitoring the status of the malware scanning system.

%nafiseh's intro stuff
\input{problem-definition}
