\section{Specification} To aid in the task of designing the solution, a set of
requirements have been drawn up. These requirements have been derived from the
division of the task presented in the goals of the project with MOSCOW priority
attached to each.

\begin{enumerate} \setlength{\itemsep}{1pt}
    \item The system \textbf{must} be able to collect trends.
    \item The system \textbf{should} be able to collect trends from more than once source.
    \item The system \textbf{must} be able to discover target web pages using a search engine .
    \item The system \textbf{should} be able to discover target web pages using multiple different search engines.
    \item The system \textbf{could} be able to discover target web pages using Twitter.
    \item The system \textbf{must} be able to determine if a page is malicious or not.
    \item The system \textbf{wont} detect ad-ware and made for ad-sense pages.
    \item The system \textbf{wont} detect Phishing.
    \item The system \textbf{must} be able to control multiple different malware scanning components.
    \item The system \textbf{must} use High Interaction malware Scanning.
    \item The system \textbf{must} use Zero Interaction malware Scanning.
    \item The system \textbf{must} use Low Interaction malware Scanning.
    \item The system \textbf{should} be able to dispatch dispatch only likely candidate malicious URLs to slower High Interaction Scanners.
    \item The system \textbf{should} be able to fine tune High Interaction Scanner dispatch probability.
    \item The system \textbf{could} use historical speed and current status of the system to influence High Interaction Scanner dispatch probability.
    \item The system \textbf{must} be able to store data determined about targets.
    \item The system \textbf{must} be able to relate data about targets to the
    trend source and time it was discovered on.
    \item The system \textbf{must} be able to generate reports.
    \item The system \textbf{should} be able to show the time taken for a particular.
    \item The system \textbf{could} display reports dynamically using a web based interface.
    \item The system \textbf{should} be able to monitor the status of the system.
    \item The system \textbf{should} be able to monitor the status of each malware scanning component.
    \item The system \textbf{could} be able to display statuses with a web interface.
\end{enumerate}

\section{Customer Interaction} The project was put forward by Team Cymru
Research NFP, ``a specialized Internet security research firm and 501(c)3
non-profit''\cite{team-cymru}. Team Cymru maintains various real-time monitoring
``pods'' to measure the status of malware on the public Internet. The project
compliments their existing offerings by incorporating social media and news
trends with active web scanning.

Over the course of the project the group had two meetings with Team Cymru
representative Chas Tomlin: a video conference and an informal meeting.
Meetings were intended to occur at the start of the project and after each of
the presentations, however only one of the post-presentation meetings occurred.

The video conference was used to introduce the group to Team Cymru and discuss
the project requirements, in which the brief was expanded upon. The
specification was influenced by requests to: 

\begin{enumerate}
    \item A requirement to emulate a user browsing the web using a virtualized
            web browser also referred to as High Interaction Malware Scanning.

    \item A requirement to use simple crawling and static analysis as in Low
        Interaction Malware Scanners, to be determined as part of the literature
        search.

    \item A suggestion to create a scanning modules that uses signature oriented
        scanning of pages and the hyper-linked files

    \item A suggestion to write modules that make use of existing repositories
        of malicious websites such as Google's Safe Browsing
        API\cite{google-safe} Google's Safe Browsing API and the crowd sourced
        Web Of Trust.

    \item Make the code machine-independant, so as to allow the scanning modules
        to operate on cheap, commodity, cloud machines such as Amazon Web
        Services Spot Instances\cite{aws-spot} or Rackspace Cloud
        instances\cite{rackspace}
\end{enumerate}

Also discussed was the possibility of downloading and investigating a ``Drive by
Download'' malicious software distribution tool.  The legal considerations of
downloading and executing an illegal piece of software are complex and as such
would require the group to obtain a detailed set of permissions before
attempting such a task.

While researching this as a possibility because of such considerations it was
determined that the time and effort required to obtain permissions to would be
prohibitive the decision was made to not investigate ``Drive By Download''
toolkits as part of the project.

After the first presentation an informal meeting was held to discuss progress on
the project so far with Chas:

\begin{enumerate} 
    \item A suggestion to use Internet Explorer 6 running under
            several interfaces of Wine to act as a faster High Interaction
            malware scanner than virtualizing an entire operating system.

    \item A suggestion to use ClamAV as the scanning engine behind the signature
        oriented scanning malware scanner.

    \item Lowered the requirement of a web based reporting interface from
        \textbf{should} to \textbf{could}, as being able to manually query the
        database would be acceptable.

    \item A requirement to be able to monitor the system, components and workers
        specifically mentioning Nagios, however it was chosen to use Celery's
        own monitoring tools instead.

    \item A requirement that the system must not focus on different types of
        malicious content such as ad-ware, made for ad-sense pages or Phishing
        sites and should instead only focus on drive by download systems.
\end{enumerate}

One further meeting was to be held after the second presentation, but Chas was
not available.

\nomenclature{API}{Application programming interface}
